\documentclass[10pt, letterpaper]{article}
% Packages
\usepackage[
    ignoreheadfoot,
    top=1.5cm,
    bottom=1.5cm,
    left=1.5cm,
    right=1.5cm,
    footskip=0.6cm
]{geometry}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
% DARK BLUE COLOR for links
\definecolor{primaryColor}{RGB}{0, 77, 153}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage[
    pdftitle={Kunal Maurya's Resume},
    pdfauthor={Kunal Maurya},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage{charter}
\raggedright
\pagestyle{empty}
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

% Titlesec format
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{2pt}\titlerule]
\titlespacing{\section}{0pt}{0.4cm}{0.2cm}

\renewcommand\labelitemi{\textbullet}
\setlist[itemize]{itemsep=3pt, topsep=4pt, leftmargin=12pt}

\begin{document}

\begin{center}
    {\Large \textbf{Kunal Maurya}} \\[4pt]
    New Delhi, India \quad | \quad +91 9319546762 \quad | \quad
    \href{mailto:kunalmaurya.mait@gmail.com}{kunalmaurya.mait@gmail.com} \\[2pt]
    \href{https://github.com/kunalmaurya-17-24}{\textbf{github.com/kunalmaurya-17-24}} \quad | \quad
    \href{https://www.linkedin.com/in/kunal-maurya-a58035304/}{\textbf{linkedin.com/in/kunal-maurya}}
\end{center}

\section{Education}
\textbf{Maharaja Agrasen Institute of Technology}, GGSIPU, Delhi \hfill \textit{2022 – May 2026 (Expected)} \\
\textbf{B.Tech in Computer Science \& Technology}

\section{Experience}
\textbf{Agentic AI Intern} — Frugal Explorations Foundation (Remote) \hfill \textit{Oct 2025 – Present}
\begin{itemize}
    \item Developing a multimodal audio RAG system fusing text, audio embeddings, and emotion metadata for querying voice data.
    \item Implementing client-side inference using \textbf{Node.js} and \textbf{transformers.js}, benchmarking Whisper vs. Wav2Vec for edge-device latency.
    \item Designing hybrid retrieval pipelines (Dense + Sparse) to fuse acoustic features with semantic text context.
    \item Engineering the RAG workflow to capture speaker diarization and emotion, enabling metadata-filtered vector search.
\end{itemize}

\textbf{Web Development Intern} — Infits (Remote) \hfill \textit{Sep 2024 – Dec 2024}
\begin{itemize}
    \item Engineered backend services for a job-finding platform using Node.js, Express, and MySQL, serving a real-time React frontend.
    \item Designed and optimized 15+ RESTful API endpoints, implementing input validation and error handling middleware.
    \item Integrated Cloud Firestore to handle real-time data synchronization between the mobile app and server.
\end{itemize}

\section{Projects}
\textbf{ATS Resume Tailoring Agent} | \textit{Python, LangGraph, Docker, FastAPI} \hfill \href{https://github.com/kunalmaurya-17-24/ATS-Resume-Tailorer}{GitHub}
\begin{itemize}
    \item Architected an autonomous agent that parses JDs and rewrites LaTeX resumes, reducing manual customization time by \textbf{80\%}.
    \item Implemented \textbf{KeyBERT} for low-cost keyword extraction before triggering expensive LLM rewriting calls, optimizing token usage.
    \item Designed a \textbf{LangGraph} state machine to validate output structure, ensuring 100\% compilation success for generated LaTeX.
    \item Deployed as a Dockerized FastAPI service with semantic scoring metrics to quantify resume-to-JD alignment.
\end{itemize}

\textbf{YouTube Multimodal RAG Pipeline} | \textit{Python, ChromaDB, yt-dlp, Streamlit} \hfill \href{https://github.com/kunalmaurya-17-24/youtube-rag}{GitHub}
\begin{itemize}
    \item Built a video QA system capable of citing specific timestamps by preserving temporal metadata during vector ingestion.
    \item Solved long-context fragmentation using timestamp-aligned semantic chunking rather than arbitrary token splitting.
    \item Integrated hybrid retrieval (Vector + Keyword) to improve specific terminology recall from auto-generated captions.
    \item Reduced hallucination rates by forcing the LLM to strictly ground answers in retrieved context chunks.
\end{itemize}

\section{Technical Skills}
\textbf{Languages:} Python, JavaScript/TypeScript, C++, SQL \\
\textbf{AI Engineering:} RAG Architectures, LangChain, LangGraph, Hugging Face, transformers.js, Vector DBs (Chroma/FAISS) \\
\textbf{Backend \& DevOps:} Node.js, Express, FastAPI, Docker, REST APIs, Git \\
\textbf{Tools:} Streamlit, KeyBERT, yt-dlp, Postman, LaTeX

% Renamed to "Certifications" so listing Udemy is honest and safe
\section{Certifications \& Awards}
\begin{itemize}
    \item \textbf{Google Arcade 2024 (Winter):} Champion milestone for coding performance.
    \item \textbf{Generative AI with Large Language Models} (Udemy)
    \item \textbf{The Complete 2024 Web Development Bootcamp} (Udemy)
\end{itemize}

\end{document}
